### 2013-12-01 index.Rmd
Some Sunday evening edits..

% Attributions for Poverty in Post-Socialist Countries
% Markus Kainu & Mikko Niemelä
% Nov 2013

`generated at:`
```{r, echo=FALSE}
Sys.time()
```
---

<link href="http://markuskainu.fi/material/css/rmarkdown.css" rel="stylesheet" type="text/css" title="compact"></link> <link href='http://fonts.googleapis.com/css?family=Oswald' rel='stylesheet' type='text/css'>

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013")
library(kaRski)
knitpandoc("index")

cd ~/workspace/lits/attrib/attrib_year2013/
lftp -u np16003 -e "mput *.html *.Rmd *.pdf;quit" ftp://np16003@www.muuankarski.org/domains/muuankarski.org/public_html/research/attributions/

cd ~/workspace/lits/attrib/attrib_year2013/figure
lftp -u np16003 -e "mirror -R;quit" ftp://np16003@www.muuankarski.org/domains/muuankarski.org/public_html/research/attributions/figure

cd ~/workspace/lits/attrib/attrib_year2013/moscow2013
lftp -u np16003 -e "mput *.html;quit" ftp://np16003@www.muuankarski.org/domains/muuankarski.org/public_html/research/attributions/moscow2013

cd ~/workspace/lits/attrib/attrib_year2013/turku2013
lftp -u np16003 -e "mput *.html;quit" ftp://np16003@www.muuankarski.org/domains/muuankarski.org/public_html/research/attributions/turku2013
```

@@

`log of changes`

date      comment
--------  -------------------
20131103  Regression modelling in process. Final models will be published on Tuesday afternoon
20131105  Regression modelling almost finished. Bug in a software caused a delay. Will be fixed by Wed morning. Now the tables are there, but coef and model names are not customized.
20131106  Regression modelling somewhat done for Turku seminar.
20131109  Corrections from Turku and the text restuctured. Methods needs to be opened
20131111  Presentation for HSE conference and improving the text a bit

>>>>

# Attributions for Poverty in Post-Socialist Countries - Markus Kainu & Mikko Niemelä

****

@@

### 2013-12-01 loadClean.Rmd
Some Sunday evening edits..

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(knitr)
library(markdown)
knit2html('loadClean.Rmd', 
          stylesheet="~/workspace/web/css/rmarkdown.css",
          options = c('toc', markdown::markdownHTMLOptions(TRUE)))

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=TRUE,eval=TRUE, cache=FALSE,message=FALSE,warning=FALSE,fig.width=12,fig.height=12)
```

@@

```{rLoadClean6, eval=TRUE}
### Dependent var country level values
## 2010
library(survey)
d.df <- svydesign(id = ~SerialID, weights = ~weight, data = df)
q309_10 <- data.frame(prop.table(svytable(~q309 + cntry, d.df), 2) * 100)
q309_10 <- q309_10[!is.na(q309_10$Freq), ]
q309_10w <- dcast(q309_10, cntry ~ q309, value.var="Freq")
names(q309_10w) <- c("cntry","socialBlame",
                        "individualBlame","individualFate",
                        "socialFate","notStated","dontKnow")

@@

poverty_06 <- data.frame(prop.table(svytable(~poverty + cntry, d.df), 
                                        2) * 100)
poverty_06 <- poverty_06[!is.na(poverty_06$Freq), ]
poverty_06w <- dcast(poverty_06, cntry ~ poverty, value.var="Freq")
names(poverty_06w) <- c("cntry","socialBlameRec","individualBlameRec",
                        "individualFateRec","socialFateRec")
## perGini
library(laeken)
perGini2006 <- as.data.frame(gini(inc="q211_rec",
                      weights = "weight_1",
                      data = lits1,
                      na.rm = TRUE,
                      breakdown="cntry")[2])

>>>>

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=TRUE,eval=TRUE, cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=12)
```

@@

```{rLoadClean6, eval=TRUE}
### Dependent var country level values
## 2010
library(reshape2)
library(survey)
d.df <- svydesign(id = ~SerialID, weights = ~weight, data = df)
q309_10 <- data.frame(prop.table(svytable(~q309 + cntry, d.df), 2) * 100)
q309_10 <- q309_10[!is.na(q309_10$Freq), ]
q309_10w <- dcast(q309_10, cntry ~ q309, value.var="Freq")
names(q309_10w) <- c("cntry","socialBlame",
                        "individualBlame","individualFate",
                        "socialFate","notStated","dontKnow")

@@

poverty_06 <- data.frame(prop.table(svytable(~poverty + cntry, d.df), 
                                        2) * 100)
poverty_06 <- poverty_06[!is.na(poverty_06$Freq), ]
poverty_06w <- dcast(poverty_06, cntry ~ poverty, value.var="Freq")
names(poverty_06w) <- c("cntry","socialBlameRec","individualBlameRec",
                        "individualFateRec","socialFateRec")
## perGini
library(laeken)
perGini2006 <- as.data.frame(gini(inc="q211_rec",
                      weights = "weight",
                      data = lits1,
                      na.rm = TRUE,
                      breakdown="cntry")[2])
